\bf Faster Neural Machine Translation Inference

### 2018-02-02 fast-beam/fast-beam.tex
fast beam paper

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		  & Europarl		& OpenSubtitles \\ \hline
\# sentences  	  & 30,000 		& 50,000 \\
\# subwords 	  & 787,908 		& 467,654 \\ 
Avg subwords/sent & 26.3		& 9.4 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:corpora}
\end{table}

@@

The results are better when translating the OpenSubtitles test set, Figure~\ref{fig:topup-opensubtitles}. The top-up batching does not harm performance when used with maxi-batching, even helping a little for small beams. However, it increases translation speed by up to 12\% when used alone.

@@

>>>>

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		  & Europarl		& OpenSubtitles \\ \hline
\# sentences  	  & 30,000 		& 50,000 \\
\# subwords 	  & 787,908 		& 467,654 \\ 
Avg subwords/sent & 26.3		& 9.4 \\
Std dev subwords/sent & 14.9		& 6.1 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:corpora}
\end{table}

@@

The results are better when translating the OpenSubtitles test set, Figure~\ref{fig:topup-opensubtitles}. The top-up batching does not harm performance when used with maxi-batching, even helping a little for small beams. However, top-up batching increases translation speed by up to 12\% when used alone.

@@

The gain from top-up batching is partially dependent on how much time the standard mini-batching algorithm spend decoding with a very small number of sentences as this is does not fully utilize the GPU cores. From Figure~\ref{fig:batch-size-small}, 20\% of the decoding iterations have less than 8 sentences remaining in the batch when translating the Europarl test test with maxi-batching. This figure is 50\% for the OpenSubtitles test set with no maxi-batching. The OpenSubtitles test set has a higher variance of sentence lengths relative to its average sentence length, which forces the mini-batch algorithm to continue decoding with a small number of sentences while the other sentences have already completed.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size-small.png}} 
\end{tabular}
\caption{Actual batchsize during decoding}
\label{fig:batch-size-small}
\end{figure}
